Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2015-12-02 tmm.tex
Add explanation to LEM and its verification experiment

While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems that need to be primarily addressed when adopting SVC in adaptive video streaming. First, as the prerequisite of bitrate adaption, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained. This is called the bitstream extraction problem. Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate. Second, when the bandwidth changes with time, it is necessary to make decisions about whether and how to adjust the video quality or bitrate. This problem is called quality control, which means controlling the video quality (or the bitrate, from the transmission point of view) to follow the change of the bandwidth. A good quality control algorithm should determine a suitable bitrate according to current network condition, and keep the video quality both smooth and at a high level.

@@

Quality control is the second problem we will address in this paper. The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality delieverd the user. In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed. Even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.

For a quality control algorithm, there are three targets that should be achieved. First is to ensure the continuity of video playing. In real-time streaming system, each data packet has its own playtime, which is also regarded as the deadline of the transmission. If the packet does not arrive at client side before the deadline, the media player will be paused due to lack of data, and that should be avoided. The second is to keep a smooth video quality. Although network conditions may change rapidly, it is necessary for the streamed video to maintain a relatively stable quality level, since frequent change of video quality will lead to poor user experience. The third target is to make the video quality as good as possible. In other words, the available bandwidth should be fully utilized. Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback will pause nor any quality fluctuation will happen. However, a low video quality is certainly not what we want.

The state-of-the-art solutions to avoid video pause in client media player mainly focus on how to select and schedule the video packets. In \cite{Gao06}, K. Gao et al. proposed a priority based scheduling strategy which guarantees packets of higher importance will be transmitted earlier. Among the packets with the same priority, those having the earliest deadline will be transmitted first. A similar solution is proposed in \cite{Schierl10}, where video data is pre-buffered in several buffers of different priorities. Whenever re-buffering occurs, quality will be degraded to a lower level to meet the time and rate constraint. Although the priority based scheduling strategies perform well in maintaining a non-paused video playing, they do not take quality fluctuation into account. As a result, users may still suffer from the frequent fluctuation of video quality.

In the widely-used video streaming server DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet). When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set thresholds to judge whether and how violently the quality change should be made. This algorithm can reduce quality fluctuation to some degree. However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops. Furthermore, this algorithm does not keep track of the bandwidth change so it cannot adjust the video quality accordingly. Quality oscillation might occur in this algorithm.

The following of this paper will present our solution for each of the problems in detail. The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system. It should be noted that, in practical video streaming systems there are other issues that need to be addressed. One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality. How to avoid or even recover from packet loss/error is an important research topic that is popular in both networking and multimedia community. However, in this paper which focuses on server-side adaptation, packet loss is not handled and we simply assume that the video stream will be successfully delivered to the client.

@@

In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}, neglecting any rounding, clipping, and deblocking filtering operation. According to this feature, the main steps in H.264/AVC coding -- prediction, transform and quantization -- are proximately linear operations, and the whole coding process can be expressed in a matrix format as follows:
\begin{equation}
\label{eq:linear}
s = {\rm\bf M} \cdot s + {\rm\bf T} \cdot c + p \: ,
\end{equation}
It means, the reconstructed samples of a Group of Pictures (GOP), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor. In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that the product ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residual values. The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen Quantization Parameter (QP) values.

We apply the above linear decoding model to the case of quality scalability of SVC and get a Linear Error Model (LEM). According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
\begin{equation}
\label{eq:base0}
s_{B} = {\rm\bf M} \cdot s_{B} + {\rm\bf T}_{B} \cdot c_{B} + p \: ,
\end{equation}
where the subscript $B$ indicates the base layer variables. In quality scalability, the enhancement is mainly the refinement of transform coefficients, so for a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
\begin{equation}
\label{eq:subset1}
s_{I_1} = {\rm\bf M} \cdot s_{I_1} + {\rm\bf T}_{B} \cdot c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i \cdot c_i \Big) + p \: ,
\end{equation}
where $i$ refers to an enhancement packet as an element of $I_1$. $c_i$ is a vector containing coefficients within the enhancement packet $i$. ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$. ${\rm\bf T}_i \cdot c_i$ gives the residual sample values decoded from $i$.

@@

Obviously, $e_j$ is only determined by packet $j$, and has no relation with other enhancement packets. This value is called the ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$. We can obtain the error vector of each enhancement packet by subtraction between video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $. Once all packets' error vectors are obtained, the distortion caused by discarding a group of packets can be estimated by adding up the error vector of each packet in the group.

@@

It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time. In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained independently at the same time.

@@

Consider a video bitstream with 8-frame GOPs shown in Fig. \ref{fig:GOP_Structure}. Base layer packets are colored black, and enhancement packets with the same color are allocated in one group. In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other. For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7 (frame number starts from 0). So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs. Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames. To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$. For the example in Fig. \ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$. However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame'' \cite{H264Overview} (e.g. frame 0, 8, 16, etc.) packets. The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs. As an instance, the loss of packet 4 would propagate drift into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20). So key frame enhancement packets within the same quality layer (e.g. packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4). Therefore, the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}. Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.

@@

Based on the linear error model described above, we can obtain error vectors of all enhancement packets. Then we can estimate the distortion caused by discarding any set of enhancement packets, by adding up the error vector of each packet in that set.

@@

Before using the linear error model, we conduct an experiment to verify it. All bitstreams in the experiment are encoded with the JSVM encoder, where the same GOP structure as illustrated in Fig. \ref{fig:GOP_Structure} and CABAC entropy coding are used. Each bitstream contains one base layer and one enhancement layer, with QP = 33 and QP = 27, respectively. The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively). Random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal. One comparison result for the test sequence {\em Foreman} (only first 33 frames are used) is shown in Fig. \ref{fig:model_verification}. The horizontal axis stands for frame index, and the vertical axis for MSE measurement. The solid line represents the actual distortion for the frames, and the dot line represents the distortion estimated by the proposed linear error model. It can be seen that the two lines are very close to each other, which demonstrates the accuracy of estimation using the proposed model. Estimation errors for all the eight SVC standard test sequences are listed in Table \ref{tab:estimation-error}, which shows that the average error is only about 5\%.

@@

In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction. Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution. Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact. A packet's R-D impact is mathematically measured by:
\begin{equation}
\label{eq:rd_impact}
\Phi_{i} = \dfrac{\partial D}{\partial R} \: ,
\end{equation}
where $\partial D$ represents the distortion change brought by discarding this packet, and $\partial R$ is the corresponding rate change. $\partial R$ is simply equivalent to the size of this packet, while $\partial D$ needs to be calculated by subtraction of distortions before and after the packet is discarded.

@@

The detailed discarding and priority assignment process is described below:
\begin{description}
\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$.
\item[2)] Within the packets that can be discarded, find the packet $m$ having the least RD impact on the sequence, \textit{i.e. }
\begin{equation}
\label{eq:R-D_impact_m}
\Phi_m = \min_{i \in I_{top}} \Phi_i \: ,
\end{equation}
where $I_{top}$ stands for the top-layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
\begin{equation}
\label{eq:R-D_impact_i}
\Phi_i = \dfrac{\partial D}{\partial R} = \dfrac{PSNR(e_{seq}) - PSNR(e_{seq} + e_i)}{SIZE(i)} \: ,
\end{equation}
where $PSNR(*)$ means to obtain PSNR from the error vector, and $SIZE(i)$ is the size of packet $i$.
\item[3)]The packet, $m$, is then removed from the bitstream, and its error vector is added to the sequence's error vector, \textit{i.e.}
\begin{equation}
\label{eq:error_update}
e_{seq} = e_{seq} + e_m \: .
\end{equation}
\item[4)]The process from 2) to 3) is repeated until all enhancement packets are discarded, and every packet is assigned a priority value according to the removing order.
\end{description}

>>>>

While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems that need to be primarily addressed in the SVC adaptive video streaming system. First, as the prerequisite of bitrate adaption, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained. This is called the bitstream extraction problem. Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate. Second, when the bandwidth changes with time, it is necessary to make decisions about whether and how to adjust the video quality or bitrate. This problem is called quality control, which means controlling the video quality (or the bitrate, from the transmission point of view) to follow the change of the bandwidth. A good quality control algorithm should determine a suitable bitrate according to current network condition, and keep the video quality both smooth and at a high level.

@@

Quality control is the second problem we will address in this paper. The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of the video quality delivered to the user. In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed. Even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.

For a quality control algorithm, there are three targets to be achieved. The first is to ensure the continuity of video playing. In real-time streaming system, each data packet has its own playtime, which is also regarded as the deadline of the transmission. If the packet does not arrive at client side before the deadline, the media player will be paused due to lack of data, and that should be avoided. The second is to keep a smooth video quality. Although network conditions may change rapidly, it is necessary for the streamed video to maintain a relatively stable quality level, since frequent change of video quality will lead to poor user experience. The third target is to make the video quality as good as possible. In other words, the available bandwidth should be fully utilized. Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback will pause nor any quality fluctuation will happen. However, a low video quality is certainly not what the user want.

The state-of-the-art solutions to avoid playback pause in client media player mainly focus on how to select and schedule the video packets. In \cite{Gao06}, K. Gao et al. proposed a priority based scheduling strategy which guarantees packets of higher importance will be transmitted earlier. Among the packets with the same priority, those having the earliest deadline will be transmitted first. A similar solution is proposed in \cite{Schierl10}, where video data is pre-buffered in several buffers of different priorities. Whenever re-buffering occurs, quality will be degraded to a lower level to meet the time and rate constraint. Although the priority based scheduling strategies perform well in maintaining a non-paused video playing, they do not take quality fluctuation into account. As a result, users may still suffer from the frequent fluctuation of video quality.

In the widely-used video streaming server DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet). When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set thresholds to judge whether and how violently the quality change should be made. This algorithm can reduce quality fluctuation to some degree. However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops. Furthermore, this algorithm does not keep track of the bandwidth change so it can only adjust the video quality based on current state. Quality oscillation might occur in this algorithm.

The following of this paper will present our solution for each of the problems. The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system. It should be noted that, in practical streaming systems there are other issues to be addressed. One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality. How to avoid or even recover from packet loss/error is an important research topic that is popular in both networking and multimedia community. However, in this paper which focuses on server-side adaptation, packet loss is not handled and the video stream is assumed to be successfully delivered to the client.

@@

In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}. According to this feature, the main steps of decoding -- prediction, transform and quantization -- are proximately linear operations (neglecting any rounding, clipping, and deblocking filtering), and the whole process can be expressed in a matrix format as follows:
\begin{equation}
\label{eq:linear}
s = {\rm\bf M} \cdot s + {\rm\bf T} \cdot c + p \: ,
\end{equation}
It means, the reconstructed samples of a Group of Pictures (GOP), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residuals, and a static predictor. In (\ref{eq:linear}), $c$ refers to the transform coefficients and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residuals. The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen Quantization Parameter (QP).

We apply the above linear decoding feature to the case of quality scalability of SVC and get a Linear Error Model (LEM). According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
\begin{equation}
\label{eq:base0}
s_{B} = {\rm\bf M} \cdot s_{B} + {\rm\bf T}_{B} \cdot c_{B} + p \: ,
\end{equation}
where the subscript $B$ indicates the base layer variables. In quality scalability, the enhancement is mainly the refinement of transform coefficients, so for a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
\begin{equation}
\label{eq:subset1}
s_{I_1} = {\rm\bf M} \cdot s_{I_1} + {\rm\bf T}_{B} \cdot c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i \cdot c_i \Big) + p \: ,
\end{equation}
where $i$ refers to an enhancement packet in the set $I_1$. $c_i$ is a vector containing coefficients within the enhancement packet $i$. ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$. ${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.

@@

Obviously, $e_j$ is only determined by packet $j$, and has no relation with other enhancement packets. The value $e_j$ is defined as ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$. We can obtain the error vector of each enhancement packet by subtraction between video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $. Once all enhancement packets' error vectors are obtained, the distortion caused by discarding a set of enhancement packets can be estimated by adding up the error vector of each packet in the set. For example, if enhancement packets $k$, $l$, $n$ are removed from a bitstream, then the difference of the reconstruction before and after the removal is supposed to be $e = e_k + e_l + e_m$. The reason for this sum to be rational is twofold: first, unlike MSE or PSNR, error vector is simply the difference of raw pixel values, with no quadratic calculation ever involved; second, each enhancement packet adds its own refinement to the pixel values during the reconstruction, due to the linear feature of the decoding process (see the derivation above). The second point is conditionally true though, as noted below.

@@

It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time. In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained at the same time.

@@

Consider a video bitstream with 8-frame GOPs shown in Fig. \ref{fig:GOP_Structure}. Base layer packets are colored black, and enhancement packets with the same color are allocated in one group. In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they can cause are not interfered with each other. For example, the removal of packet 8 would cause pixel errors only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7 (frame index starts from 0). So we can do subtraction only once for this group, to obtain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs. Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames. To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$. For the example in Fig. \ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the extraction-and-decoding number is $(3 - 1) \times 4 = 8$. However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame'' \cite{H264Overview} (e.g. frame 0, 8, 16, etc.) packets. The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs. As an instance, the loss of packet 4 would propagate error into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20). So key frame enhancement packets within the same quality layer (e.g. packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4). Therefore, the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}. Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.

@@

Based on the LEM, we can estimate the distortion caused by discarding any set of enhancement packets, by adding up the error vector of each packet in that set.

@@

Before using the estimation based on LEM, we conduct an experiment to verify it. All bitstreams in the experiment are encoded with the JSVM encoder, where the GOP structure as illustrated in Fig. \ref{fig:GOP_Structure} and the CABAC entropy coding are used. Each bitstream contains one base layer and one enhancement layer, with QP = 33 and QP = 27, respectively. The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively). Random combinations of enhancement packets are removed from a bitstream, and the distortion estimated by the linear error model are compared with the actually calculated distortion. Decoding is performed by JSVM decoder, and distortion estimation or calculation is done by Matlab. One comparison result for the test sequence {\em Foreman} (only first 33 frames are used) is shown in Fig. \ref{fig:model_verification}. The horizontal axis stands for frame index, and the vertical axis for MSE measurement. The solid line represents the actual distortion for the frames, and the dot line represents the distortion estimated by the proposed linear error model. It can be seen that the two lines are very close to each other, which demonstrates the accuracy of estimation using the proposed model. Estimation errors for all the eight SVC standard test sequences are listed in Table \ref{tab:estimation-error}, which shows that the average error is only about 5\%.

@@

In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction. A greedy-like \cite{GreedyAlgo} bitstream extraction algorithm is proposed. Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact. A packet's R-D impact is mathematically measured by:
\begin{equation}
\label{eq:rd_impact}
\Phi_{i} = \dfrac{\partial D}{\partial R} \: ,
\end{equation}
where $\partial D$ represents the distortion change brought by discarding this packet, and $\partial R$ is the corresponding rate change. $\partial R$ is simply equivalent to the size of this packet, while $\partial D$ needs to be calculated by subtraction of distortions before and after the packet is discarded.

@@

The detailed discarding and priority assignment process is described below:
\begin{description}
\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$, which is $e_{full}$ is defined in Eqation \).
\item[2)] Within the packets that can be discarded, find the packet $m$ having the least RD impact on the sequence, \textit{i.e. }
\begin{equation}
\label{eq:R-D_impact_m}
\Phi_m = \min_{i \in I_{top}} \Phi_i \: ,
\end{equation}
where $I_{top}$ stands for the top-layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
\begin{equation}
\label{eq:R-D_impact_i}
\Phi_i = \dfrac{\partial D}{\partial R} = \dfrac{PSNR(e_{seq}) - PSNR(e_{seq} + e_i)}{SIZE(i)} \: ,
\end{equation}
where $PSNR(*)$ means to obtain PSNR from the error vector, and $SIZE(i)$ is the size of packet $i$.
\item[3)]The packet, $m$, is then removed from the bitstream, and its error vector is added to the sequence's error vector, \textit{i.e.}
\begin{equation}
\label{eq:error_update}
e_{seq} = e_{seq} + e_m \: .
\end{equation}
\item[4)]The process from 2) to 3) is repeated until all enhancement packets are discarded, and every packet is assigned a priority value according to the removing order.
\end{description}
